%
%Academic CV LaTeX Template
% Author: Dubasi Pavan Kumar
% LinkedIn: https://www.linkedin.com/in/im-pavankumar/
% License: MIT
%
% For errors, suggestions, or improvements, please contact:
% Email: pavankumard.pg19.ma@nitp.ac.in
%

\documentclass[a4paper,11pt]{article}

% Package imports
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage{fontawesome5}

% Color definitions
\definecolor{darkblue}{RGB}{0,0,139}

% Page layout
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
\setlength{\footskip}{5pt} % Addressing fancyhdr warning

% Hyperlink setup (moved after fancyhdr to address warning)
\usepackage[hidelinks]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,
    urlcolor=darkblue,
}

% Custom box settings
\usepackage[most]{tcolorbox}
\tcbset{
    frame code={},
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!20,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=-2mm,
    boxsep=4pt,
    arc=0pt,outer arc=0pt,
}

% URL style
\urlstyle{same}

% Text alignment
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabularx}{0.98\textwidth}{@{}L r@{}}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}}
    \end{tabularx}
    \vspace{-6.0mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabularx}{0.98\textwidth}[t]{@{}L r@{}}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \small\textbf{#3} &  \footnotesize{#2}\\
    \end{tabularx}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabularx}{0.98\textwidth}[t]{@{}L r@{}}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \small\textbf{#2} & \footnotesize{#4}
    \end{tabularx}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\circ$}}$}

% Fixed left margins so every bullet sits at a deterministic column.
% Using leftmargin=* made the bullet x-position depend on each item's content
% (the tabularx body), so entry bullets drifted between sections and did not
% line up. Explicit margins pin the entry bullets and the nested item bullets.
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=3.4mm,labelsep=1mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=3.4mm,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=3.6mm,labelsep=1mm,itemsep=0.5mm]}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-3mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%

% Commands for icon sizing and positioning
\newcommand{\socialicon}[1]{\raisebox{-0.05em}{\resizebox{!}{1em}{#1}}}
\newcommand{\ieeeicon}[1]{\raisebox{-0.3em}{\resizebox{!}{1.3em}{#1}}}

% Font options
\newcommand{\headerfonti}{\fontfamily{phv}\selectfont} % Helvetica-like (similar to Arial/Calibri)
\newcommand{\headerfontii}{\fontfamily{ptm}\selectfont} % Times-like (similar to Times New Roman)
\newcommand{\headerfontiii}{\fontfamily{ppl}\selectfont} % Palatino (elegant serif)
\newcommand{\headerfontiv}{\fontfamily{pbk}\selectfont} % Bookman (readable serif)
\newcommand{\headerfontv}{\fontfamily{pag}\selectfont} % Avant Garde-like (similar to Trebuchet MS)
\newcommand{\headerfontvi}{\fontfamily{cmss}\selectfont} % Computer Modern Sans Serif
\newcommand{\headerfontvii}{\fontfamily{qhv}\selectfont} % Quasi-Helvetica (another Arial/Calibri alternative)
\newcommand{\headerfontviii}{\fontfamily{qpl}\selectfont} % Quasi-Palatino (another elegant serif option)
\newcommand{\headerfontix}{\fontfamily{qtm}\selectfont} % Quasi-Times (another Times New Roman alternative)
\newcommand{\headerfontx}{\fontfamily{bch}\selectfont} % Charter (clean serif font)

\begin{document}
% Allow page breaks anywhere: fill page 1 completely and let sections
% continue onto the next page (no widow/orphan/heading-break protection).
\raggedbottom
\widowpenalty=0
\clubpenalty=0
\interlinepenalty=0
\brokenpenalty=0
\predisplaypenalty=0
\postdisplaypenalty=0
\interfootnotelinepenalty=0
% Forbid breaking right before a section heading, so a heading is never
% pushed to the next page on its own; the page fills and breaks mid-section.
\makeatletter
\@secpenalty=10000
\makeatother
\headerfontiii

% Header
\begin{center}
    {\Huge\textbf{LI ZIHAO}}
\end{center}
\vspace{-6mm}

\begin{center}
    \small{
    +86 13618297005 | \href{mailto:lizihao2023@lzu.edu.cn}{lizihao2023@lzu.edu.cn} | 
    \href{https://chiselli.com}{chiselli.com}
    }
\end{center}
\vspace{-6mm}

\begin{center}
    \small{
    \socialicon{\faGithub} \href{https://github.com/MiShenng}{MiShenng} | 
    \socialicon{\faFacebookF} \href{https://www.facebook.com/chiselli}{chiselli} | 
    \socialicon{\faBookOpen} \href{https://www.douban.com/people/MiShenng}{Douban}
    }
\end{center}
\vspace{-6mm}

%----------------------------------------------------------------------------------------
%   EDUCATION
%----------------------------------------------------------------------------------------
\section{\textbf{Education}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeSubheading
{Lanzhou University}{Lanzhou}
{B.A. in Journalism}{Sep. 2023 - Present}
\resumeItemListStart
\item \textbf{Relevant Coursework:} New Media User Analysis, Communication Psychology, Media Criticism, Research Methods in Communication Studies, Data Journalism, Introduction to Communication Studies, Public Opinion
\item \textbf{GPA:} \href{https://mybolg-lizao.vercel.app/media/pdfs/lanzhou_transcript_en.pdf}{4.06/5.0}
\resumeItemListEnd

\resumeSubheading
{National Taiwan Normal University}{Taipei}
{Exchange Student}{Aug. 2025 - Dec. 2025}
\resumeItemListStart
\item \textbf{Relevant Coursework:} Visual Culture and Communication, Research Method of Social Science, New Media and Society Seminar
\item \textbf{GPA:} \href{https://mybolg-lizao.vercel.app/media/pdfs/taiwan_transcript.pdf}{3.9/4.0}
\resumeItemListEnd

\resumeSubHeadingListEnd

%----------------------------------------------------------------------------------------
%   PUBLICATIONS
%----------------------------------------------------------------------------------------
\section{\textbf{Peer-reviewed publications \& Conference Papers}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeProject
  {Should I Stay Calm: How Does the Combination of Visual and Textual Frames Influence Expressions of Anger in Short Video Comment Sections?}
  {Li, Zihao.*}
  {AEJMC 2026}
  {{}[\href{https://github.com/MiShenng/visual_textual_frames_anger}{\textcolor{darkblue}{\faGlobe}}]}
\resumeItemListStart
  \item This study develops a computational method for identifying visual frames in dynamic short videos, applied to 449 Douyin videos on China's drug record sealing controversy alongside 419,126 user comments. Both visual and textual content are classified into intensifying, informational, and mitigating frames, while a fine-tuned BERT classifier detects anger at the comment level.
  \item Results show that visual and textual frames within individual videos tend to align rather than diverge, and that different frame combinations correspond to significantly different levels of comment anger. Two-way ANOVA confirms that both modalities independently contribute to anger in an additive fashion without significant interaction, suggesting that emotional responses are jointly organized across modalities rather than driven by a single channel.
\resumeItemListEnd

\resumeSubHeadingListEnd


%----------------------------------------------------------------------------------------
\section{\textbf{Working Papers}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeProject
  {See It, Click It? How Visual Clickbait Shapes Stratified User Engagement in Health-Related Videos on China's Bilibili}
  {Li, Zihao.*}
  {RIP}
  {{}[\href{https://github.com/MiShenng/Bilibili-Health-Visual-Clickbait}{\textcolor{darkblue}{\faGlobe}}]}
\resumeItemListStart
  \item This study examines how visual clickbait in health-related video thumbnails shapes stratified user engagement on Bilibili. Using 22,323 videos collected through 28 Chinese health-related keywords, it analyzes thumbnails, titles, video metadata, and platform-native engagement metrics including views, likes, coins, and favorites.
  \item The project combines human annotation, LLM-assisted classification, semi-supervised machine learning, and Chinese-CLIP image--text similarity to measure visual clickbait cues and thumbnail--title semantic congruence. By distinguishing low-cost attention from high-cost endorsement, the study investigates whether visual clickbait can increase exposure without producing stronger forms of user approval.
\resumeItemListEnd

\resumeSubHeadingListEnd

%----------------------------------------------------------------------------------------
%   RESEARCH EXPERIENCE
%----------------------------------------------------------------------------------------
\section{\textbf{Research Experience}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeSubheading
  {A Study on Discourse Construction and Visual Narrative Strategies in the New Mainstream Media Environment of the Converged Media Era}{{}[\href{https://github.com/MiShenng/An_Analysis_of_Environmental_Discourse_in_Peoples_Daily}{\textcolor{darkblue}{\faGlobe}}]}
  {Research Assistant \textbar{} PI: Li Xinxin, Lanzhou University}{Dec. 2024 - Apr. 2025}
\resumeItemListStart
  \item Using reports from People’s Daily as representative examples of mainstream media, I constructed a dataset of environmental news coverage from 1949 to the present. I then developed an LLM-driven automated content analysis program to perform coding. Drawing on Fairclough’s discourse analysis methodology and situating the coding results within the evolution of China’s environmental protection policies, I divided the historical development of China’s environmental protection discourse into distinct phases and developed the analysis into a research paper.
  \item Using a self-built web crawler to collect Weibo posts related to environmental protection from the People's Daily to date, and conducted a comparative analysis of this data with content from the newspaper's print editions.
\resumeItemListEnd

\resumeSubheading
  {A Study on the ``Human-Machine Co-creation'' Mechanism and Innovative Practices in AI-Empowered Cultural Narratives Along the Silk Road}
  {}
  {Research Assistant \textbar{} PI: Li Xinxin, Lanzhou University}{Mar. 2025 - May. 2025}
\resumeItemListStart
\item Compiled and organized narrative materials on the historical development of the Silk Road.
\item Synthesized research trends in Silk Road studies across multiple social science disciplines and developed them into a comprehensive literature review.
\resumeItemListEnd

\resumeSubheading
  {Lanzhou Bathing Assistant: Seeing Aging at Mobile Bathhouses}{{}[\href{https://some-link.com}{\textcolor{darkblue}{\faGlobe}}]}
  {Field Research \textbar{} Advisor: Shiping, Lanzhou University}{Aug. 2024 - Jan. 2025}
\resumeItemListStart
 \item Conducted ethnographic field research on the emerging in-home elder-bathing industry in Lanzhou, focusing on disabled and bedridden older adults’ experiences of bodily dignity, care, and social invisibility under China’s home-based eldercare model.
\item Conducted participant observation and semi-structured interviews with the company founder, bathing assistants, eldercare-center managers, and family caregivers. Analyzed how demographic change, local climate, economic conditions, bathing culture, and cultural attitudes toward aging shaped the industry’s development in northwest China, resulting in an in-depth written report and a short video documentary.
\resumeItemListEnd

\resumeSubheading
  {Why Do College Students Have a Particular Affinity for Life ``Within the System''?}
  {}
  {Student Research \textbar{} Advisor: Zhangchi, Lanzhou University}{Apr. 2024 - Apr. 2025}
\resumeItemListStart
  \item Investigated the behavioral mechanisms driving Chinese college students' intensifying preference for public-sector employment. Co-designed the survey instrument, oversaw questionnaire distribution and data collection, and performed statistical analysis to isolate key predictors of career-choice behavior.
  \item Complemented quantitative findings with semi-structured interviews, triangulating survey data with personal narratives to unpack the motivations fueling the civil-service-exam craze (\textit{kaogong} fever) and to formulate evidence-based policy recommendations.
\resumeItemListEnd

\resumeSubHeadingListEnd


%----------------------------------------------------------------------------------------
%   AWARDS
%----------------------------------------------------------------------------------------
\section{\textbf{Selected Awards and Honors}}
\vspace{-0.4mm}
\resumeSubHeadingListStart
\resumePOR{China Data Journalism Competition}
    {, \textit{Second Prize} [\href{https://www.chiselli.com/images/\%E6\%95\%B0\%E6\%8D\%AE\%E6\%96\%B0\%E9\%97\%BB\%E5\%A4\%A7\%E8\%B5\%9B.jpg}{\textcolor{darkblue}{\faGlobe}}]}
    {Nov. 2025}
\resumePOR{China Statistical Modeling Competition, Lanzhou University Campus Round}
    {, \textit{Second Prize} [\href{https://github.com/MiShenng/Mathematics_and_Statistical_Modeling_Competition_Record/tree/main/2026_China_Statistical_Modeling_Competition}{\textcolor{darkblue}{\faGlobe}}]}
    {May. 2026}
\resumePOR{Central China Mathematical Modeling Competition}
    {, \textit{Second Prize} [\href{https://github.com/MiShenng/Mathematics_and_Statistical_Modeling_Competition_Record/tree/main/2026_Huazhong_Cup_Mathematical_Modeling_Competition}{\textcolor{darkblue}{\faGlobe}}]}
    {May. 2026}
\resumePOR{China University Campus Media Competition}
    {, \textit{Public Service Communication Award} [\href{https://www.chiselli.com/images/\%E6\%A0\%A1\%E5\%9B\%AD\%E5\%AA\%92\%E4\%BD\%93\%E5\%A4\%A7\%E8\%B5\%9B.jpg}{\textcolor{darkblue}{\faGlobe}}]}
    {Nov. 2025}
\resumePOR{14th China Tower Journalists' Day}
    {, \textit{Grand Prize in the Communications Category} [\href{https://www.chiselli.com/images/\%E9\%93\%81\%E5\%A1\%94\%E8\%AE\%B0\%E8\%80\%85\%E8\%8A\%82.jpg}{\textcolor{darkblue}{\faGlobe}}]}
    {Dec. 2025}
\resumePOR{Lanzhou University Outstanding Student Scholarship}
    { [\href{https://www.chiselli.com/images/\%E4\%B8\%89\%E7\%AD\%89\%E5\%A5\%96\%E5\%AD\%A6\%E9\%87\%91.jpg}{\textcolor{darkblue}{\faGlobe}}]}
    {Sep. 2023 - Sep. 2024}
\resumeSubHeadingListEnd

%----------------------------------------------------------------------------------------
%   SKILLS
%----------------------------------------------------------------------------------------
\section{\textbf{Skills}}
\vspace{-0.4mm}
 \resumeHeadingSkillStart
  \resumeSubItem{Programming:}
    {R, Python, web development (HTML, CSS), AI4SS}
  \resumeSubItem{Quantitative Methods:}
    {Fundamentals of probability and statistics, regression, ANOVA}
  \resumeSubItem{Computational Methods:}
    {Natural language processing, automated content analysis, topic modeling, machine learning, image-as-data}
  \resumeSubItem{Qualitative Methods:}
    {Interviews, coding, content analysis, field research}
  \resumeSubItem{Languages:}
    {Mandarin (Native), English (Good)}
  \resumeSubItem{Production Tools:}
    {\LaTeX, Microsoft Office Suite, photography}
 \resumeHeadingSkillEnd

\end{document}
